---
output:
  github_document:
    fig_width: 12
    fig_height: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning = FALSE, message = FALSE, echo = FALSE}
library(magrittr)
```

# hrgraphsign
```
Simplifies analysis of hr-graph data based on the six signatures
from this article: https://hbr.org/2018/11/better-people-analytics

```

## Installation
```
devtools::install_github("mrtnnrdlnd/hrgraphsign")
```

## Background
There are measures of employees performance which can't be measured in isolation.
Six of these measures are mentioned in the article: 

> **Better People Analytics**
> Measure who they know, not just who they are. **by Paul Leonardi and Noshir Contractor**

This package is an attempt to make these six measures a little easier to use in practice.
The measures is referred to as signatures in the article and so they will be here.
They are, in order of appearance:

1. **Ideation Signature** - Individual level measure
2. **Influence Signature** - Individual level measure
3. **Efficiency Signature** - Team level measure
4. **innovation Signature** - Team level measure
5. **Silo Signature** - Organizational level measure
6. **Vulnerability Signature** Organizational level measure

## The Signatures by example
Before getting to the actual signatures we load some example data and create a connected network from it

### Example Data

```{r, warning = FALSE, message = FALSE}
# nodes will be representing the employees
nodes <- readxl::read_excel("example/nodes.xlsx")
# Look at data
knitr::kable(nodes %>% head(5))
```

```{r, warning = FALSE, message = FALSE}
# edges will be representing the relations between the employees
edges <- readxl::read_excel("example/edges.xlsx")
# Look at data
knitr::kable(edges %>% head(5))
```

### Create Graph

```{r, warning = FALSE, message = FALSE}
example_graph <- edges %>% 
  dplyr::select(FromID, ToID, everything()) %>%
  igraph::graph_from_data_frame(directed = FALSE, vertices = nodes) %>% 
  hrgraphsign::aggregate_edges()
```

### Individual level

#### Ideation Signature
Predicts, according to the article, which employees will come up with good ideas.

The ideation signature is measured by having a low value of something called **Burt's constraint**, named after Ronald Stuart Burt. It looks at how widespread connections and how much connections to different groups a person has.

```{r, warning = FALSE, message = FALSE}
# Get ideation measure
igraph::V(example_graph)$ideation <- hrgraphsign::ideation_signature(example_graph)
# Display Top 3 For Ideation
knitr::kable(hrgraphsign::get_top_by_column(example_graph, column = "ideation", n = 3))
```

#### Influence Signature
Predicts, according to the article, Which employees will change others’ behavior

Measures how connected connections a person has.

Note: Implementation is vague


```{r, warning = FALSE, message = FALSE}
# Get influence measure
igraph::V(example_graph)$influence <- hrgraphsign::influence_signature(example_graph)
# Display Top 3 For Influence
knitr::kable(hrgraphsign::get_top_by_column(example_graph, column = "influence", n = 3))
```

#### Comparison
```{r, warning = FALSE, message = FALSE}
set.seed(5)
layout1 <- igraph::layout.fruchterman.reingold(example_graph)
par(mfrow = c(1,2))
plot(example_graph,
     edge.width = igraph::E(example_graph)$weights,
     vertex.color = hrgraphsign::vertices_colors(example_graph, attribute = "department"),
     vertex.size = hrgraphsign::vertices_sizes(example_graph, attribute = "ideation"),
     main = "Ideation",
     layout = layout1
     )
plot(example_graph,
     edge.width = igraph::E(example_graph)$weights,
     vertex.color = hrgraphsign::vertices_colors(example_graph, attribute = "department"),
     vertex.size = hrgraphsign::vertices_sizes(example_graph, attribute = "influence"),
     main = "Influence",
     layout = layout1
)
```

### Team Level

```{r, warning = FALSE, message = FALSE}
# Create subgraph for teams to measure
teams <- c("Engineering", "Marketing", "Sales")

engineering_team <- example_graph %>%
  igraph::induced_subgraph(., igraph::V(.)[igraph::V(.)$department == "Engineering"])
marketing_team <- example_graph %>%
  igraph::induced_subgraph(., igraph::V(.)[igraph::V(.)$department == "Marketing"])
sales_team <- example_graph %>%
  igraph::induced_subgraph(., igraph::V(.)[igraph::V(.)$department == "Sales"])

```

#### Efficiency Signature
Predicts, according to the article, Which teams will complete projects on time.

The efficiency signature is a combination of a team with **high density**, and
at the same time have **high external range** which means having members that are well connected to different sources outside the team.

```{r, warning = FALSE, message = FALSE}
# Get measure
efficiency <- c(
  hrgraphsign::efficiency_signature(example_graph, engineering_team),
  hrgraphsign::efficiency_signature(example_graph, marketing_team),
  hrgraphsign::efficiency_signature(example_graph, sales_team)
)

knitr::kable(data.frame(teams, efficiency))
```
#### Innovation Signature
Predicts, according to the article, Which teams will innovate effectively.

The innovation signature is a combination of a team with **low density** and
at the same time have **high external range** or **wide, diverse connections**.

```{r, warning = FALSE, message = FALSE}
# Get measure
innovation <- c(
  hrgraphsign::innovation_signature(example_graph, engineering_team),
  hrgraphsign::innovation_signature(example_graph, marketing_team),
  hrgraphsign::innovation_signature(example_graph, sales_team)
)

knitr::kable(data.frame(teams, efficiency, innovation))
```




### Misc 

#### Plot friends_friends

```{r, warning = FALSE, message = FALSE}

par(mfrow = c(1,2))
subgraph <- hrgraphsign::friends_friends(example_graph, 13, 2)
set.seed(10)
layout2 <- igraph::layout.fruchterman.reingold(subgraph)
  plot(subgraph,
       edge.width = igraph::E(example_graph)$weights,
       vertex.color = hrgraphsign::vertices_colors(subgraph, attribute = "department"),
       vertex.size = hrgraphsign::vertices_sizes(subgraph, attribute = "ideation"),
       main = "Ideation",
       layout = layout2
  )
  plot(subgraph,
       edge.width = igraph::E(example_graph)$weights,
       vertex.color = hrgraphsign::vertices_colors(subgraph, attribute = "department"),
       vertex.size = hrgraphsign::vertices_sizes(subgraph, attribute = "influence"),
       main = "Influence",
       layout = layout2
  )
```
